Verifying Cache Coherence Protocols for an Infinite Family of Cache Hierarchies

### 2014-02-06 paper/Conclusion.tex
changed ending a bit to be less terrible

Moving this work towards generating a fully verified MSI implementation requires
a number of small steps. First, the simple transliteration of descriptions
between Bluespec and Coq, must be done in a mechanical way. Second, the
compilation of Bluespec to hardware is unverified; to fully trust the
implementation the Bluespec compiler must be verified. Some initial work on this
has already been done~\cite{TDBLP:conf/cav/BraibantC13}. Finally, we must extend
our notion of correctness to apply to the hardware substrate and not just the
level of atomic transactions. Most notably, this requires the some guarantee of
liveness and fairness in handling of messages in the final design. We have
initial Coq-based proofs that with finite buffers a local fairness in
transaction our protocol will have this property, but more work is needed to
fully resolve this venture.

>>>>

Moving this work towards generating a fully verified MSI implementation requires
a number of small steps. First, the simple transliteration of descriptions
between Bluespec and Coq, must be done in a mechanical way. Second, the
compilation of Bluespec to hardware is unverified; to fully trust the
implementation the Bluespec compiler must be verified. Some initial work on this
has already been done~\cite{TDBLP:conf/cav/BraibantC13}. Finally, we must extend
our notion of correctness to apply to the hardware substrate and not just the
level of atomic transactions. Most notably, this requires the some guarantee of
liveness and fairness in handling of messages in the final design. We have
initial Coq-based proofs that with finite buffers a local fairness in
transaction our protocol will have this property, but more work is needed.
